Draft

### 2017-08-27 Thesis/Draft.tex
add hoeffding bound

\begin{itemize}
\tightlist
\item
  Show Chernoff/Hoeffding bound detailed
\item
  Show union bound to get deviation for all arms \(i \leq K\) and every
  round \(s \leq T\)
\end{itemize}

@@

@@

@@

One of the APT algorithm's main features is its simplicity. The sampling
rule is very straightforward, and, as highlighted in Locatelli et al.
(2016), it does not require any knowledge about the type of
sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
algorithm immediately applicable in practice while it still enjoys its
upper bound on the expected regret. This is in particular worth
highlighting when comparing APT to algorithms used in the pure
exploration bandit setting. There, many algorithms require knowledge
about the corresponding complexity upfront. The problem however being,
that to know the complexity, the experimenter has to know all means up
to a permutation of the arms (for example, see Audibert et al., 2010).
This, of course, is not given in practice and thus alternative
algorithms try to estimate the complexity online which is not a
desirable solution either as especially in the beginning plug-in
estimates based on the estimated means may lead to wrong estimates of
the complexity and consequently budget allocation based on mistaken
beliefs (compare Garivier and Kaufmann, 2016).

Furthermore, Locatelli et al. (2016) were able to present an upper bound
for the APT algorithm matching the lower bound in their Theorem 1.
Proofs of both bounds are given below.

Where the APT algorithm shows room for improvement is when it comes to
settings with distributions that are not sub-Gaussian. This is mentioned
in Locatelli et al. (2016). In general, the problem becomes that the
assumptions for the bounds no longer hold; furthermore, the statistic
\(B_i(t+1)\), and the term \(\hat{\Delta}_i(t)\) are motivated by
(sub-)Gaussian distributions. The more one moves away from Gaussian-like
distributions, the less appropriate this term becomes, however. In
particular, the empirical mean will be less concentrated around the true
mean and more impacted by outliers which are more likely under non
sub-Gaussian distributions. Locatelli et al. (2016) thus refers to
Bubeck et al. (2013) which considers solutions for multi-armed bandits
that are based on heavy-tail distributions. By using more robust
estimators of the mean, one could equip the APT algorithm to deal with
such distributions.

Another step towards dealing with non sub-Gaussianity is made by
Mukherjee et al. (2017) who use an estimate of the variance additionally
to the empirical mean in their Augmented UCB solution. Utilizing this
additional information, the algorithm seems to perform better than for
example APT, going from simulation results displayed in the paper.
However, the simulations deal exclusively with normal distributions, as
the variance has to be bounded for the upper bound of the Augmented UCB
to hold. We will continue to discuss the Augmented UCB solution in
chapter 3.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show
bounds based on the Kullback-Leibler divergence of the specific
distribution directly. While the approximation through the Gaussian
Kullback-Leibler divergence in the lower bound proof is convenient and
leads to the simple APT algorithm, it might not stay appropriate for
distributions whose Kullback-Leibler divergence tends to differ from the
Gaussian. This, for example, is the case for Bernoulli distributions at
very small parameters \(\mu\). By looking at the graphical examples
below it becomes obvious that the Kullback-Leibler divergence between
Bernoulli distributions starts to lose any similarity to the quadratic
approximation. The second graph then shows that the actual
Kullback-Leibler divergence of Bernoulli distributions loses any
symmetry over this range of parameter values. Given that Bernoulli
distributions with very small parameter values arise naturally in many
applications in website optimization, advertising click-through
modeling, or anomaly detection in time series, there is a need to tackle
this problem.

Refer also to page 6 in Kaufmann et al. (2016): ``This
information-theoretic lower bound permits to interpret the quantity
\(H(\nu)\) defined in (2) as a subgaussian approximation''. In the case
of Normal distributions with known and equal mean, it holds that the
Kullback-Leibler divergence between \(\nu_i\) and \(\nu_j\),
parameterized by \(\mu_i\) and \(\mu_j\), can be written as

\[
\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
\]

@@

In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
its first argument, and thus can be well approximated by Pinsker's
inequality:

@@

This shows how the distance measure used in the APT algorithm, and
consequently the complexity \(H\), is a useful approximation of the
KL-divergence for sub-Gaussian distributions. However, this
approximation suffers as the distributions less and less similar to
Gaussian distributions. Thus similarly to how UCB algorithms in the
cumulative regret setting have been extended to KL-UCB algorithms
(compare Cappé et al., 2013), also the APT algorithm offers room for
improvement.

And so a potential approach can be to use the Kullback-Leibler
divergence as measure similar to the methods proposed in Kaufmann et al.
(2015). They proposed Kullback-Leibler based approaches for the pure
exploration bandit setting, which we will describe in chapter 2. Then,
in chapter 3, we will come back to the problem of using the
Kullback-Leibler divergence in the thresholding bandit setting. To
conclude chapter 1, we proof the lower bound and upper bound for the APT
algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al.
(2016).

@@

\section{Kullback-Leibler Complexity of Pure
Exploration}\label{kullback-leibler-complexity-of-pure-exploration}

@@

\subsection{Variance Based Algorithms for Thresholding
Bandits}\label{variance-based-algorithms-for-thresholding-bandits}

\subsubsection{Augmented-UCB Algorithm}\label{augmented-ucb-algorithm}

@@

\subsubsection{Anytime Parameter-free Empirical Variance Guided
Algorithm}\label{anytime-parameter-free-empirical-variance-guided-algorithm}

@@

\subsection{Likelihood Ratio for Exponential Family
Distributions}\label{likelihood-ratio-for-exponential-family-distributions}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}

>>>>

We know that \(X_i\) are \(R\)-sub-Gaussian by assumption. That is, we
have

\[
\mathbb{E}[\exp (tX_{i,s}-t\mathbb{E}[X_{i,s}])] = \mathbb{E}[\exp (t(X_{i,s}-\mathbb{E}[X_{i,s}]))] \leq \exp (R^2t^2/2)
\]

where the RHS is the moment-generating function of the random variable
\(X_{i,s}-\mathbb{E}[X_{i,s}]\). While Höffding's Lemma and Höffding's
Inequality are commonly applied to bounded random variables \(Z\) with
\(\mathbb{P}(a\leq Z \leq b) = 1\) and \(\mathbb{E}[Z] = 0\), we see
that \(Z\) are \(R\)-sub-Gaussian with \(R^2 = \frac{(a-b)^2}{4}\).
Using this last equality, we can easily apply Höffding's Inequality to
our case.

\begin{lemma}[Höffding's Inequality (Kloft Lecture Notes)] \label{lemma:HoeffdingsInequality}
Let $X_1, ..., X_s$ be independent, identically distributed random variables with mean $\mathbb{E}[X_t] = \mu$ and $\mathbb{P}(a_t \leq X_t - \mathbb{E}[X] \leq b_t) = 1$. Denote their empirical mean by $\bar{X}_s=\frac{1}{s}\sum_{t=1}^{s}X_t$. Then, for any $\gamma > 0$, we have the following concentration inequality:

\begin{equation*}
\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-2s^2\gamma^2/\sum_{t=1}^s(b_t - a_t)^2).
\end{equation*}
\end{lemma}

If we replace \(\sum_{t=1}^s(b_t - a_t)^2\) by \(4sR^2\), we have the
concentration inequality for our \(R\)-sub-Gaussian random variables:

\[
\mathbb{P}(|\bar{X}_s - \mu| \geq \gamma) \leq 2\exp (-\frac{s\gamma^2}{2R^2}).
\]

Writing \(\gamma = \sqrt{\frac{T\delta^2}{Hs}}\), we get for the
favorable event
\(\xi_i = \{|\bar{X}_s - \mu| \leq \sqrt{\frac{T\delta^2}{Hs}}\}\) of an
individual arm \(i\), for each \(i \in \mathbb{A}\) and each
\(s \in \{1, ..., T\}\):

\[
\mathbb{P}(\xi_i) = \mathbb{P}\Big(|\bar{X}_{i,s} - \mu_i| \leq \sqrt{\frac{T\delta^2}{Hs}}\Big) \geq 1 - 2\exp (-\frac{T\delta^2}{2R^2H}),
\] where \(T\) is again the total budget of samples, and \(H\) the
complexity. Now let

\[
\tilde{\xi} = \Big\{\forall i \in \mathbb{A}: |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
\]

To derive the probability of event \(\tilde{\xi}\), we apply a union
bound on \(\mathbb{P}(\cup_{i=1}^K \xi_i^C)\):

\begin{align*}
\mathbb{P}(\tilde{\xi}) & = & 1-\mathbb{P}(\xi^C) \\
& = & 1-\mathbb{P}(\cup_{i=1}^K \xi_i^C) \\
& \geq & 1 - \sum_{i=1}^K \mathbb{P}(\xi_i^C) \\
& \geq & 1 - 2K\exp (-\frac{T\delta^2}{2R^2H})
\end{align*}

We could use the same union bound a second time to bound over all
\(s \in \{1, ..., T\}\) and derive for the favorable event \(\xi\):

\[
\mathbb{P}(\xi) \geq 1 - 2TK \exp(-\frac{T\delta^2}{2R^2H})
\]

Locatelli et al. (2016) use instead of Höffding's inequality a
Sub-Gaussian martingale inequality including a peeling argument in order
to derive a better bound of

@@

This bound is non-trivial for much smaller values of \(T\), and we will
use it in the following.

@@

We now present the lower bound given in Locatelli et al. (2016) for the
thresholding bandit problem. In order to derive the bound, a problem is
specified to show that the error of the lower bound is attained even in
this specific problem. In particular, for a set of problems with
Gaussian distributions of variance \(1\), the largest probability of
error on these problems that the best algorithm exhibits is still at
least as large as the lower bound.

@@

One of the APT algorithm's main features is its simplicity. The sampling
rule is very straightforward, and, as highlighted in Locatelli et al.
(2016), it does not require any knowledge about the type of
sub-Gaussianity \(R\), or the complexity \(H\) upfront. This makes the
algorithm immediately applicable in practice while it still enjoys its
upper bound on the expected regret. This is in particular worth
highlighting when comparing APT to algorithms used in the best arm
identification or Top-\(m\) setting. As alluded to in
\autoref{sec:TheAPTAlgorithm}, many algorithms that fix the sampling
budget upfront (i.e., fixed budget algorithms as UCB-E or KL-LUCB-E)
require knowledge about the corresponding complexity upfront (Audibert
et al., 2010; Kaufmann and Kalyanakrishnan, 2013). The problem however
being, that to know the complexity, the experimenter has to know all
means up to a permutation of the arms. This, of course, is not given in
practice. Thus alternative algorithms try to estimate the complexity
online which can be difficult as especially in the beginning plug-in
estimates based on the estimated means may lead to wrong estimates of
the complexity, which in turn leads to poor budget allocation based on
mistaken beliefs (compare Garivier and Kaufmann, 2016). On the other
hand, the sequential sampling strategy has to rely on some estimate.
While the APT algorithm does not explicitly estimate the complexity, the
gaps that serve as index are essentially the same. Faced not with
sub-Gaussian but more heavy-tailed distributions, these estimates might
well lead to poor performance.

Here, the APT algorithm shows room for improvement, as also mentioned in
Locatelli et al. (2016). The problem is that the assumptions for the
bounds no longer hold as arms are less sub-Gaussian; of course the
complexity \(H\) and the term \(\hat{\Delta}_i(t)\) in the algorithm's
index are motivated by sub-Gaussian distributions. The more one moves
away from those, the less appropriate these quantities become. In
particular, the empirical mean will be less (or not at all) concentrated
around the true mean and more impacted by outliers which are more likely
under non sub-Gaussian distributions. Locatelli et al. (2016) thus
refers to Bubeck et al. (2013a) which considers solutions for
multi-armed bandits that are based on heavy-tail distributions. By using
more robust estimators of the mean, one could equip the APT algorithm to
deal with such distributions.

Both Mukherjee et al. (2017) as well as Zhong et al. (2017) use
estimates of the variance of the arms for their algorithms for the
thresholding bandit problem and try to thereby improve upon the
performance of the APT algorithm. While their simulations show promising
results, their bounds rely on the assumption of bounded reward
distributions. Thus their algorithms are not necessarily able to improve
upon the assumption of sub-Gaussian distributions made by Locatelli et
al. (2016). We will continue to discuss their results in
\autoref{chap:VarianceBasedAlgorithms}.

Yet another idea, again mentioned in Locatelli et al. (2016) is to show
bounds based on the Kullback-Leibler divergence of the specific
distribution directly. While the approximation through the Gaussian
Kullback-Leibler divergence in the lower bound proof is convenient and
leads to the simple APT algorithm, it might not stay appropriate for
distributions whose Kullback-Leibler divergence tends to differ from the
Gaussian. This, for example, is the case for Bernoulli distributions at
very small parameters \(\mu\). We have for the Kullback-Leibler
divergence of two Gaussian distributions \(\nu_i\) and \(\nu_j\) of mean
\(\mu_i\) and \(\mu_j\) with equal variance:

\[
\KL_{N}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
\]

@@

In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
its first argument, and thus can be relatively well approximated by
Pinsker's inequality (SHOW IN GRAPH!):

@@

This is of course equal to the Gaussian KL-divergence described before.
This approximation, however, suffers for heavily for very small values
of \(\mu_i\) and \(\tau\). In particular, the Bernoulli KL-divergence
becomes asymmetric in its first argument as \(\tau \neq 0.5\). Thus, in
contrast to the complexity measure \(H\) based on the Gaussian
KL-divergence, a complexity measure based on the Bernoulli KL-divergence
would evaluate two arms as differently difficult if their absolute
distance to the threshold is the same, but they lie on different sides
of the threshold.

Thus similarly to how UCB algorithms in the cumulative regret setting
have been extended to KL-UCB algorithms (compare Cappé et al., 2013),
also the APT algorithm offers room for improvement. As a more explicit
example of such adaptation, consider the case of Top-\(m\)
identification described in Kaufmann et al. (2016). The authors develop
a lower bound based on KL-divergence, and note that ``This
information-theoretic lower bound permits to interpret the quantity
\(H(\nu)\) {[}\ldots{}{]} as a subgaussian approximation''. Given that
Bernoulli distributions with very small parameter values arise naturally
in many applications, an improvement in this regard would be valuable.

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and Top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.

@@

\section{\texorpdfstring{Kullback-Leibler Complexity of Pure Exploration
\label{chap:KullbackLeiblerPureExploration}}{Kullback-Leibler Complexity of Pure Exploration }}\label{kullback-leibler-complexity-of-pure-exploration}

@@

\subsection{\texorpdfstring{Variance Based Algorithms for Thresholding
Bandits
\label{chap:VarianceBasedAlgorithms}}{Variance Based Algorithms for Thresholding Bandits }}\label{variance-based-algorithms-for-thresholding-bandits}

\subsubsection{\texorpdfstring{Augmented-UCB Algorithm
\label{sec:AugUCBAlgorithm}}{Augmented-UCB Algorithm }}\label{augmented-ucb-algorithm}

@@

\subsubsection{\texorpdfstring{Anytime Parameter-free Empirical Variance
Guided Algorithm
\label{sec:EVTAlgorithm}}{Anytime Parameter-free Empirical Variance Guided Algorithm }}\label{anytime-parameter-free-empirical-variance-guided-algorithm}

@@

\subsection{\texorpdfstring{Likelihood Ratio for Exponential Family
Distributions
\label{sec:LikelihoodRatioForExponentialFamily}}{Likelihood Ratio for Exponential Family Distributions }}\label{likelihood-ratio-for-exponential-family-distributions}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-2.pdf}
